---
title: "PA3"
date:  "Last update:`r Sys.Date()`"
author: "La Ramirez"
Output: html_document
editor_options: 
  chunk_output_type: console
output: 
  html_document: 
    highlight: zenburn
    theme: sandstone
---


```{r, 'setup', message=FALSE}
library("tidyverse")
library("untidydata")
library("languageR")
library("dplyr")
library("stringr")

```




```{r, out.width="100%", fig.retina=2}
primingHeidPrevRT %>%
  mutate(One = stringr::str_replace(RTmin1, "RTmin1", "1")) %>% 
  mutate(Two = stringr::str_replace(RTmin2, "RTmin2", "2")) %>%
  mutate(Three = stringr::str_replace(RTmin3, "RTmin3", "3")) %>%
  mutate(Four = stringr::str_replace(RTmin4, "RTmin4", "4")) %>%
  gather(key = "RTmin", value = "Score", One:Four) %>% 
   ##deleting the columns that have been pivoted
  select(-RTmin1, -RTmin2, -RTmin3, -RTmin4) %>% 
  ##calculating some descriptive statistics
  group_by(LengthInLetters) %>% 
  summarize(
    avg = mean(RT),
    sd = sd(RT),
    min = min(RT),
    max= max(RT)
    ) 
   ##calculating bivariate regression
   model <- lm(RT ~ RTtoPrime, data=primingHeidPrevRT) 
   summary(model) 
   ##Generate a plot
  primingHeidPrevRT %>% 
     ggplot() +
     ##aes (x = RTtoPrime, y = LengthInLetters) +
     aes (x = RT, y = RTtoPrime) +
     geom_point() +
     geom_smooth(method = "lm")
  
  
  
```
Some comments about this assignment:

The residuals -errors- of this model show a min of -0.66401 and a max of 0.89910, which is a wide range and therefore the predictions made based on this model might not be too accurate. We also have a negative median, which means most of the residuals are negative. 

In the linear regression model, RT and RTtoPrime seem to be related with an Intercept of 3.86138 and a slope of 0.41148, that is, for every increase of one in the Y axis -the independent variable, the X axis -dependent variable, increases 0.41148. Therefore, and as seen in the graphic, there seems to be a positive relationship between both variables.
